Understanding the impacts of video-guided activities on parent-child interaction

### 2020-03-26 paper/manuscript.tex
Mike and Emily edits, fixed NAs

53 infants (F = 38, M = 15) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
Fifteen parents reported that their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).

@@

Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2018).
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55,0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11,0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32,0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11,0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24,0.82{]} for rate (seconds per minute) of coordinated JA episodes.

@@

Parents' child-directed speech during the play sessions was transcribed.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

For each transcript, the words were lemmatized using \texttt{spacy2} (Honnibal, 2017), and the word \emph{types} (unique words) and \emph{tokens} (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by McCarthy \& Jarvis (2010): 0.720).

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior falls.
There was lower TTR in the Activity Video condition (mean: 0.33) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.05{]}).
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 18.55) than in the No Video condition (mean: 27.09, \(\beta=\)-8.48, 95\% CI={[}-15.48,-1.45{]}), with no predicted influence of age.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 19.45, 95\% CI={[}8.93,30.24{]}), with parents using more words in the Activity Video condition (mean: 60, bootstrapped 95\% confidence interval (conf. int.): {[}193,259{]}) than in the No Video condition (mean: 41, 95\% conf. int.: {[}139,194{]}).

@@

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.15,1.27{]}).
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.65,-0.02{]}).
However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.11,1.04{]}).

To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
Words that are strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that are most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable:
after the Activity Video, parents used more words related to requests (e.g., \enquote{Can I have X? / Give me X. Thank you!}), whereas after no intervention parents' language related more to invitations (e.g., \enquote{Are you ready?} / \enquote{Let's see.}).
However, parents who watched an activity video also made more bids for JA with their child.
While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.

@@

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.\footnote{Preregistration: \url{https://osf.io/2bpdf/}.}

@@

84 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
Sixteen parents reported their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).

@@

The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session.
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1.
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48,0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61,0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44,0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75,0.94{]} for total duration of coordinated JA episodes.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15,-0.04{]}).
The preregistered regression predicting the number of tokens used by parents revealed no effects.
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.20, 95\% conf. int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 95\% CI = {[}0.39,1.64{]}) than after the Science Video (mean: 3.18, 95\% conf. int.: {[}2.81, 3.54{]}).
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 95\% CI = {[}0.08,0.93{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf. int.: {[}2.61, 3.15{]}) than after the Control Video (mean: 2.36, 95\% conf. int.: {[}2.13, 2.61{]}).
Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 95\% CI = {[}-2.64,-0.37{]}).
However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 95\% CI = {[}-0.02,3.23{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 95\% CI = {[}0.06,0.84{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
There was an interaction of age and condition (\(\beta=1.60\), 95\% CI = {[}0.15,3.18{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.

Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 95\% CI = {[}-1.64,0.02{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 95\% CI = {[}-0.01,0{]}).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that are strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that are most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.

@@

We were interested in how digital parenting advice alters parents' interactions with their children.
We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions.
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2).
In some cases--especially in older children--these bids were successful in increasing engagement.
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}) whereas control conditions featured more invitational words (e.g., \enquote{say}, \enquote{let}, \enquote{like}), often asking about animal noises (\enquote{What does the X say?}).

@@

\leavevmode\hypertarget{ref-Hembacher2018}{}%
Hembacher, E., \& Frank, M. C. (2018). The early parenting attitudes questionnaire: Measuring intuitive theories of parenting and child development. \emph{PsyArXiv}. \url{http://doi.org/10.31234/osf.io/hxk3d}

>>>>

60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
Fifteen parents reported that their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).

@@

Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
The two coders had a reliability of ICC = 0.79 with 95\% confidence interval (CI) = {[}0.55, 0.91{]} for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95\% CI = {[}-0.11, 0.67{]} for rate of passive JA episodes (per minute); ICC = 0.66 with 95\% CI = {[}0.32, 0.85{]} for rate of coordinated JA episodes; ICC = 0.33 with 95\% CI = {[}-0.11, 0.67{]} for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95\% CI = {[}0.24, 0.82{]} for rate (seconds per minute) of coordinated JA episodes.

@@

Parents' child-directed speech during the play sessions was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

For each transcript of child-directed speech, the words were lemmatized using \texttt{spacy2} (Honnibal, 2017), and the word \emph{types} (unique words) and \emph{tokens} (total words) were then tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity.
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by McCarthy \& Jarvis (2010): 0.720).

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior falls.
There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.14, 95\% CI={[}-0.29, 0.01{]}).
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-6.76, 95\% CI={[}-26.25, 12.20{]}), with no predicted influence of age.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding an effect of condition on the number of word tokens (\(\beta=\) 34.34, 95\% CI={[}0.26, 67.83{]}), with parents using more tokens in the Activity Video condition (mean: 61, bootstrapped 95\% confidence interval (conf. int.): {[}193,259{]}) than in the No Video condition (mean: 41, 95\% conf. int.: {[}139,194{]}).

@@

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Parents' bid rate was greater in the Activity Video condition (mean: 1.83, sd: 0.79) than in the No Video condition (mean: 1.10, sd: 0.83, \(\beta=0.71\), 95\% CI={[}0.15, 1.27{]}).
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA (seconds per minute of play).
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, only the regression predicting the rate of passive JA episodes showed an effect involving these demographic variables: parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=NA\), 95\% CI={[}-0.65, -0.02{]}).
However, higher RR parents in the Activity Video condition did not show a decrease in passive JA (interaction of condition and RR: \(\beta=0.60\), 95\% CI={[}0.11, 1.04{]}).

To better understand the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable:
after the Activity Video, parents used more words related to requests (e.g., \enquote{Can I have X? / Give me X. Thank you!}), whereas after no intervention parents' language related more to invitations (e.g., \enquote{Are you ready?} / \enquote{Let's see.}).
However, parents who watched an activity video also made more bids for JA with their child.
While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, expand the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.

@@

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}

@@

84 infants (F = 36, M = 46) aged 12-24 months
(20 12-17.9 month-olds in the Activity Video condition;
21 12-17.9 month-olds in the Science Video condition;
22 18-24 month-olds in the Activity Video condition;
21 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1.
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent.
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
Sixteen parents reported their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 2), four-year college (n = 36), some graduate school (n = NA), to completed graduate school (n = NA) or declined to state (n = 13).

@@

The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session.
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1.
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages.
The two coders had a reliability of ICC = 0.81 with 95\% confidence interval (CI) = {[}0.62,0.91{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.48, 0.88{]} for number of passive JA episodes; ICC = 0.80 with 95\% CI = {[}0.61, 0.91{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.44, 0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75, 0.94{]} for total duration of coordinated JA episodes.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15, -0.04{]}).
The preregistered regression predicting the number of tokens used by parents revealed no effects.
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: 4.20, 95\% conf. int.: {[}3.81, 4.63{]}; \(\beta=1.02\), 95\% CI = {[}0.39, 1.64{]}) than after the Science Video (mean: 3.18, 95\% conf. int.: {[}2.81, 3.54{]}).
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition (\(\beta=0.50\), 95\% CI = {[}0.08, 0.93{]}), with JA episodes occurring at a greater rate after the Activity Video (mean: 2.86, 95\% conf. int.: {[}2.61, 3.15{]}) than after the Control Video (mean: 2.36, 95\% conf. int.: {[}2.13, 2.61{]}).
Older children also participated in JA episodes at a lesser rate than younger children (\(\beta=-1.55\), 95\% CI = {[}-2.64, -0.37{]}).
However, this age effect was moderated in the Activity Video condition (\(\beta=1.70\), 95\% CI = {[}-0.02, 3.23{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition (\(\beta=0.46\), 95\% CI = {[}0.06, 0.84{]}), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: 2.18, 95\% CI: {[}1.89, 2.47{]}) than after the Control Video (mean: 1.72, 95\% CI: {[}1.53, 1.94{]}).
There was an interaction of age and condition (\(\beta=1.60\), 95\% CI = {[}0.15, 3.18{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.

Older children both engaged in episodes of passive JA at a greater rate with their caregiver (\(\beta=-0.88\), 95\% CI = {[}-1.64, 0.02{]}), and spent more time in passive JA with their caregiver (\(\beta=-0.01\), 95\% CI = {[}-0.01, 0{]}).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that were strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that were most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.

@@

We were interested in how digital parenting advice alters parents' interactions with their children.
We specifically set out to test whether activity suggestions led to higher-quality play, a presupposition of many early parenting interventions.
Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
In two experiments, we found that activity videos increased the rate of parents' bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2).
In some cases---especially in older children---these bids were successful in increasing engagement.
We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}) whereas control conditions featured more invitational words (e.g., \enquote{say}, \enquote{let}, \enquote{like}), often asking about animal noises (\enquote{What does the X say?}).

@@

\leavevmode\hypertarget{ref-Hembacher2020}{}%
Hembacher, E., \& Frank, M. C. (2020). The early parenting attitudes questionnaire: Measuring intuitive theories of parenting and child development. \emph{Collabra: Psychology}, \emph{6}(1). \url{http://doi.org/10.31234/osf.io/hxk3d}
